Explore Vegetation Data

### 2016-01-09 explore_veg_data.Rmd
Changes to investigation lines of code.

# I think I should work this backwards so that the most recent sampling is added to
pid2005 %in% pid2004# COOK02 is the only duplicate in the 2004 sampling
filter(alt_sp_2004, PlotID=="COOK02")
filter(alt_sp_2005, PlotID=="COOK02")
# But there are a lot more records in the 2004 data, which is closer to the 2012 & 2014 sampling. I could combine the 2004 & 2005 data, including the potentially duplicated COOK02 data.
summary(filter(alt_sp_2012, PlotID=="COOK02"))
filter(alt_sp_2014, PlotID=="COOK02")

@@

alt_sp_2014 <- rbind(alt_sp_2014, alt_sp_2012)
summary(alt_sp_2014)
summary(alt_sp_2005)
alt_sp_2005$year <- 2005

@@

# Create data frames of live and dead stems for '2005' and '2014' samplings. In reality the 2005 grouping has data from visits during 2003 and 2004, and the 2014 grouping includes data from some visits in 2012.
alt_sp_2014_live <- filter(alt_sp_2014, Dead == 0)
alt_sp_2014_live <- select(alt_sp_2014_live, -Dead)
alt_sp_2005_live <- filter(alt_sp_2005, Dead == 0)
alt_sp_2005_live <- select(alt_sp_2005_live, -Dead)
alt_sp_2014_dead <- filter(alt_sp_2014, Dead == 1)
alt_sp_2014_dead <- select(alt_sp_2014_dead, -Dead)
alt_sp_2005_dead <- filter(alt_sp_2005, Dead == 1)
alt_sp_2005_dead <- select(alt_sp_2005_dead, -Dead)

>>>>

# I think I should work this backwards so that the most recent sampling is added to
pid2005 %in% pid2004# COOK02 is the only duplicate in the 2004 sampling
filter(alt_sp_2004, PlotID=="COOK02")
filter(alt_sp_2005, PlotID=="COOK02")
# But there are a lot more records in the 2004 data, which is closer to the 2012 & 2014 sampling. I could combine the 2004 & 2005 data, including the potentially duplicated COOK02 data.
# summary(filter(alt_sp_2012, PlotID=="COOK02"))
# filter(alt_sp_2014, PlotID=="COOK02")

@@

alt_sp_2014 <- rbind(alt_sp_2014, alt_sp_2012)
summary(alt_sp_2014)
alt_sp_2014$year <- 2014
summary(alt_sp_2005)
alt_sp_2005$year <- 2005

@@

# Create data frames of live and dead stems for '2005' and '2014' samplings. In reality the 2005 grouping has data from visits during 2003 and 2004, and the 2014 grouping includes data from some visits in 2012.
alt_sp_2014_live <- filter(alt_sp_2014, Dead == 0)
alt_sp_2014_live <- select(alt_sp_2014_live, -Dead)
alt_sp_2005_live <- filter(alt_sp_2005, Dead == 0)
alt_sp_2005_live <- select(alt_sp_2005_live, -Dead)
alt_sp_2014_dead <- filter(alt_sp_2014, Dead == 1)
alt_sp_2014_dead <- select(alt_sp_2014_dead, -Dead)
alt_sp_2005_dead <- filter(alt_sp_2005, Dead == 1)# only 12 obs, all at GANAY02
alt_sp_2005_dead <- select(alt_sp_2005_dead, -Dead)
